SoyAdapt

### 2023-08-24 manuscript_soy.tex
24 aug commit

\begin{tableminipage}{\textwidth}
\begin{tabular}{|l|c|l|l|l|l|l|l|l|l}
\cline{1-9}
\multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Weir and Cockerham \\ mean Fst estimate\end{tabular}} &                & Group 1                                       & Group 2                           & Group 3                           & Group 4                           & Group 5                           & Group 6                           & Group 7                    &  \\ \cline{1-9}
                                                                                                      & Maturity group & \multicolumn{1}{c|}{SBPA}\footnote{The Maturity Group of the SBPA are not known and grouped in one group.}\\                     & \multicolumn{1}{c|}{0-0-0}        & \multicolumn{1}{c|}{0-0}          & \multicolumn{1}{c|}{0}            & \multicolumn{1}{c|}{I}            & \multicolumn{1}{c|}{II - IV}      & \multicolumn{1}{c|}{V - X} &  \\ \cline{1-9}
Group 1                                                                                               & SBPA           & \multicolumn{1}{c|}{\cellcolor[HTML]{E7E6E6}} & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}   &  \\ \cline{1-9}
Group 2                                                                                               & 0-0-0          & \cellcolor[HTML]{93CC7E}0.2968376             & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}   &  \\ \cline{1-9}
Group 3                                                                                               & 0-0            & \cellcolor[HTML]{9FD07F}0.2702235             & \cellcolor[HTML]{FBAB77}0.0306470 & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}   &  \\ \cline{1-9}
Group 4                                                                                               & 0              & \cellcolor[HTML]{B5D680}0.2212166             & \cellcolor[HTML]{FDCD7E}0.0428267 & \cellcolor[HTML]{F98B71}0.0191540 & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}   &  \\ \cline{1-9}
Group 5                                                                                               & I              & \cellcolor[HTML]{B8D780}0.2146631             & \cellcolor[HTML]{FEE983}0.0525354 & \cellcolor[HTML]{FA9D75}0.0255972 & \cellcolor[HTML]{F8696B}0.0068046 & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}   &  \\ \cline{1-9}
Group 6                                                                                               & II - IV        & \cellcolor[HTML]{8FCB7E}0.3063683             & \cellcolor[HTML]{FFEB84}0.0532384 & \cellcolor[HTML]{FCC27C}0.0387984 & \cellcolor[HTML]{FBA576}0.0282634 & \cellcolor[HTML]{FA9172}0.0212429 & \cellcolor[HTML]{E7E6E6}          & \cellcolor[HTML]{E7E6E6}   &  \\ \cline{1-9}
Group 7                                                                                               & V - X          & \cellcolor[HTML]{63BE7B}0.4046471             & \cellcolor[HTML]{F6E984}0.0745305 & \cellcolor[HTML]{F7E984}0.0728984 & \cellcolor[HTML]{FCEB84}0.0607337 & \cellcolor[HTML]{FFEB84}0.0548296 & \cellcolor[HTML]{FBAA77}0.0301916 & \cellcolor[HTML]{E7E6E6}   &  \\ \cline{1-9}
\end{tabular}
  \label{tab:fst2}
\end{tableminipage}
\end{table}

>>>>

\begin{tableminipage}{\textwidth}
\begin{tabular}{|l|c|l|l|l|l|l|l|l|l}
\cline{1-9}
\multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Weir and Cockerham \\ mean Fst estimate\end{tabular}} &
   &
  Group 1 &
  Group 2 &
  Group 3 &
  Group 4 &
  Group 5 &
  Group 6 &
  Group 7 &
   \\ \cline{1-9}
 &
  Maturity group &
  \multicolumn{1}{c|}{SBPA} &
  \multicolumn{1}{c|}{0-0-0} &
  \multicolumn{1}{c|}{0-0} &
  \multicolumn{1}{c|}{0} &
  \multicolumn{1}{c|}{I} &
  \multicolumn{1}{c|}{II - IV} &
  \multicolumn{1}{c|}{V - X} &
   \\ \cline{1-9}
Group 2 &
  0-0-0 &
  \cellcolor[HTML]{93CC7E}0.2968376 &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
   \\ \cline{1-9}
Group 3 &
  0-0 &
  \cellcolor[HTML]{9FD07F}0.2702235 &
  \cellcolor[HTML]{FBAB77}0.0306470 &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
   \\ \cline{1-9}
Group 4 &
  0 &
  \cellcolor[HTML]{B5D680}0.2212166 &
  \cellcolor[HTML]{FDCD7E}0.0428267 &
  \cellcolor[HTML]{F98B71}0.0191540 &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
   \\ \cline{1-9}
Group 5 &
  I &
  \cellcolor[HTML]{B8D780}0.2146631 &
  \cellcolor[HTML]{FEE983}0.0525354 &
  \cellcolor[HTML]{FA9D75}0.0255972 &
  \cellcolor[HTML]{F8696B}0.0068046 &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
   \\ \cline{1-9}
Group 6 &
  II - IV &
  \cellcolor[HTML]{8FCB7E}0.3063683 &
  \cellcolor[HTML]{FFEB84}0.0532384 &
  \cellcolor[HTML]{FCC27C}0.0387984 &
  \cellcolor[HTML]{FBA576}0.0282634 &
  \cellcolor[HTML]{FA9172}0.0212429 &
  \cellcolor[HTML]{E7E6E6} &
  \cellcolor[HTML]{E7E6E6} &
   \\ \cline{1-9}
Group 7 &
  V - X &
  \cellcolor[HTML]{63BE7B}0.4046471 &
  \cellcolor[HTML]{F6E984}0.0745305 &
  \cellcolor[HTML]{F7E984}0.0728984 &
  \cellcolor[HTML]{FCEB84}0.0607337 &
  \cellcolor[HTML]{FFEB84}0.0548296 &
  \cellcolor[HTML]{FBAA77}0.0301916 &
  \cellcolor[HTML]{E7E6E6} &
   \\ \cline{1-9}
\end{tabular}
  \label{tab:fst2}
\end{tableminipage}
\end{table}
